\huge Dataset-1 \normalsize\\

\begin{multicols}{2}

\section*{Hip Hop}
\subsection*{Chillhop}
\large Chillhop Essentials - Fall 2016 \normalsize\\
 01 Aso - Seasons\\ 02 The Cancel - Point\\ 03 Brock Berrigan - Owl Farm\\ 04 Philanthrope - Things Fall Apart\\ 05 GlobulDub - Hinterlands\\ 06 Guggenz - Break Even\\ 07 AJMW - Virtues\\ 08 Handbook - Swansong\\ 09 Khudosoul/Birocratic - Something Between Us (ft. Birocratic)\\ 10 Cooper Albert - Find a Way\\ 11 Nymano - Sorry\\ 12 L'Indécis - Her\\ 13 Deeb - Bridges\\ 14 Tantu - Klein\\ 15 Floppy Circus - Safari Haze\\ 16 Mecca:83 - From Summer to Autumn (Transition)\\ 17 Bonus Points - Long Exposure\\ 18 A D M B - Master of the Sun\\ 19 FloFilz - Orakel\\
\\ \large Chillhop Essentials - Spring 2017 \normalsize\\
 01 Aso - Sun In My Face\\ 02 Flamingosis - Ecstacy (Pay the Price)\\ 03 Birocratic - Sleepyface\\ 04 Mono:Massive - Attila\\ 05 saib. - spring waltz\\ 06 GYVUS - Koi\\ 07 nymano x Pandrezz - you should have known\\ 08 Limes - Cocktails\\ 09 Philanthrope - Sodium (feat. TESK)\\ 10 Juan RIOS - Colores\\ 11 Brock Berrigan - Crossing Paths\\ 12 tomppabeats - one two step\\ 13 Handbook - Rose Gardens\\ 14 Ian Ewing - Trinidad\\ 15 Devaloop x Flitz\&Suppe - Sacrifice\\ 16 Vanilla - Blue Sun\\ 17 invention - sprxng\\ 18 Elijah Nang - Haru\\ 19 Figub Brazlevic - Father \& Son\\ 20 baaskaT - stryman\\
\\ \large Chillhop Essentials - Summer 2016 \normalsize\\
 01 Guggenz - Business As Usual\\ 02 Joakim Karud - Canals\\ 03 Birocratic - Tony's Belated Breakfast\\ 04 Brock Berrigan - Split Decision\\ 05 Floppy Circus - Better Days To Come\\ 06 Handbook - Melon\\ 07 Phoniks - Touchdown\\ 08 Gorila - Heatinupyabody\\ 09 Bonus Points - Hammock Days\\ 10 Mecca:83 - Foundation\\ 11 GlobulDub - Waves\\ 12 deeB - Theme From Endless Sunset\\ 13 Imagined Herbal Flows - Beyond The Sun\\ 14 Aso - Ultra Violet\\ 15 White Lights - VR Helmet\\ 16 Philanthrope - Isolation\\ 17 Ol' Burger Beats - The Gentle Instrumental\\ 18 Jeff Kaale - Footsteps\\
\\ \large Chillhop Essentials - Winter 2016 \normalsize\\
 01 Invention - endurance\\ 02 Moose Dawa - Menti\\ 03 Birocratic - Lovely Rita\\ 04 Idealism - Snowfall\\ 05 FloFilz \& Philanthrope - Whitecap\\ 06 Melodiesinfonie - Meditation on God\\ 07 nymano - i wish i could sleep\\ 08 Juan RIOS - Pine Trees\\ 09 Mono:Massive - Blue Dawn\\ 10 L'Indécis - Rekindling\\ 11 Flitz\&Suppe - OdeToYou\\ 12 B-Side - Patience\\ 13 Aso - Caught in the Rain\\ 14 TESK - FIRST LIGHTS\\ 15 QSTN - Me 2 You\\ 16 Deeb - Flakes\\ 17 Limes - Wonderland\\
\\ \large The Essenchills Volume 1 \normalsize\\
 01 Anonymous Musik/Deeb - Loose Change (Prod. Deeb)\\ 02 Esbe - Darling\\ 03 favormusik. - serendipity.\\ 04 Stan Forebee - I'm Walkin\\ 05 L'Indécis - Monday Chill \#2\\ 06 Snow Fox Apprentice - Let It Pass\\ 07 brandon* - Sunset Heights\\ 08 Jazz Spastiks - Jazz Party\\ 09 beatmachinearon - flying in a dream\\ 10 Dezaulait - Remedy\\
\\ \large The Essenchills Volume 2 \normalsize\\
 01 saib. - Smooth\\ 02 SkyBlew/B.C.P BackPacker/AltAir - SliceOfLife (ft. B.C.P BackPacker) (Prod. AltAir)\\ 03 aso - Nothing But Luv\\ 04 Frameworks - Hillside\\ 05 Engelwood - Celebration\\ 06 PEAKOX - I Miss You\\ 07 Brock Berrigan - For Ginger\\ 08 aKu - Things To Come\\ 09 .sinh/Natty Reeves - OneForNujabes (ft. Natty Reeves)\\ 10 [DKO] - Cuddl'n\\
\\
\subsection*{Trap}
\large Monstercat \normalsize\\
 01 Pegboard Nerds - Badboi\\ 02 Aero Chord - Surface\\ 02 Aero Chord - Resistance\\ 03 Aero Chord/Anna Yvette - Break Them (feat. Anna Yvette)\\ 03 Pegboard Nerds \& NGHTMRE - Superstar (feat. Krewella)\\ 03 Grabbitz/Faustix - Friends (With Faustix)\\ 04 Pegboard Nerds/Snavs/Toby Green - Here It Comes (Snavs \& Toby Green Remix)\\ 04 Grabbitz - Ballin'\\ 06 Dirty Audio - Gorilla Glue\\ 06 Rogue - Rattlesnake\\ 06 Noisestorm - Antihero\\ 08 Razihel/TeamMate - Legends (feat. TeamMate)\\ 08 Razihel \& Aero Chord - Titans\\ 08 Snavs/Sebastian Lind - Into the Wild (feat. Sebastian Lind)\\ 10 Stonebank - Never Looking Back\\ 11 KUURO - Aamon\\ 13 Kuuro - Bandit\\ 13 Slips \& Slurs - Malicious\\ 15 Slips \& Slurs \& Holly - Turmoil\\ 16 Going Quantum x Psychic Type - Rare\\ 17 Hush - Tentakel\\ 17 Rogue - Nemesis\\ 18 Reach - Bollywood Stunna\\ 21 Varien - Nights in Bangalore Pt.2\\ 22 DotEXE - Inside Out\\ 25 Varien - Aether and Light\\
\\ \large Trap Nation Top 20 \normalsize\\
 01 Flo Rida - GDFR (K Theory Remix)\\ 02 Eiffel 65 - Blue (Da Ba Dee) [DJ Ponte Ice Pop Mix]\\ 03 Keys N Krates - Dum Dee Dum\\ 04 Chief Keef - Love Sosa\\ 05 Dillon Francis \& DJ Snake - Get Low\\ 06 T-Wayne - Nasty Freestyle\\ 07 Bobby Shmurda - Hot N*gga\\ 08 Jason Derulo - Wiggle (feat. Snoop Dogg)\\ 09 DJ Snake \& Lil Jon - Turn Down For What\\ 10  - Fifth Harmony - Worth It ft. Kid Ink (Levianth Remix)\\
\\ \large VA - Best of Trap Music [2014] \normalsize\\
 01 DJ Paimon and DJ Tetris - Enur - Calabria (DJ Paimon and\\ 02 Hudson Mohawke - Chimes\\ 03 RL Grime - Core\\ 04  - \\ 05 Louisiana Jones - Nightmare\\ 06 Knife Party - LRAD (BMBX CRTL WTF Is Festival Trap Remix).(AGRMusic)\\ 08 JiKay \& MNKN - Thug Love\\ 09 Flosstradamus - Mosh Pit (Feat. Casino).(AGRMusic)\\ 11 Martin Garrix - Animals (Riot Ten X Cazador Jungle Trap Edit).(AGRMusic)\\ 12 Bro Safari \& UFO! - Burn The Block.(AGRMusic)\\ 13 Hardwell - Spaceman (Carnage Festival Trap Remix)\\ 14 Figure - The Brown Note (Original Mix).(AGRMusic)\\ 15 Just Blaze \& Baauer Feat. Jay Z - Higher (Original Mix)\\ 16 Zeds Dead - Ratchet (Original Mix)\\ 17 Hudson Mohawke - 100HM\\ 18 Stooki Sound - Ball So Hard VIP\\ 19 Creaky Jackals - RVNNIN \\ 21 Elliphant - Revolusion (UZ Remix)\\ 22 Tomsize \& Simeon - Loud Strings\\ 23 Siméon x Tomsize - Holy Shit.(AGRMusic)\\ 24 Evil Analog ft. Anna Krista - Sweet Poison\\ 26 Tomsize - Hands In The Air (feat. Ragga Twins)\\ 27 HxV - HXV - WE COMIN feat Mac TurnUp\\ 28 Baauer \& RL Grime - Infinite Daps\\ 29 Tomsize \& Simeon - Jump (Original Mix)\\ 30 RL Grime \& Salva - Kanye West - Mercy (RL Grime \& Salva Remix)\\ 31 Keys N Krates - Dum Dee Dum (Original Mix)\\ 32 OZZIE - DOOM DADA\\ 33 Milo \& Otis - Pigeons (Original Mix)\\ 34 ETC!ETC! x Snails    - RUBBR (Original Mix) \\ 35 Skymatic - Immersion\\ 36 Snails \& Antiserum - Wild (Original Mix)\\ 37 Stellar - BOTTLES\\ 38 RL Grime \& What So Not - Tell Me\\ 39 The Chainsmokers - The Chainsmokers - \#Selfie (Botnek Remix)(Lookas Trap Edit)\\ 40 Cory Enemy - Bro Safari - The Drop (Cory Enemy Remix)\\ 41 Tomsize - Make It Rain\\ 42 Drake - 0 to 100 (Grandtheft Bootleg)\\ 43 TroyBoi x Tomsize - Ganja Man\\ 44 Woolymammoth - FLOSSTRADAMUS - UNDERGROUND ANTHEM (WOOLYMAMMOTH REMIX)\\ 45 VESTIGE - Yoppers\\ 46 Tomsize - Victor Niglio - Jager (Tomsize Remix)\\ 47 Carnage - Mara (Carnage \& Breaux Festival Trap VIP)\\
\\
\section*{House}
 \subsection*{Electro House}
\large Monstercat \normalsize\\
 01 Pegboard Nerds - New Style\\ 01 Tristam/Braken - Far Away\\ 01 Arion - Cold Blood \& Ice Cream Cones (Original Mix)\\ 01 Stephen Walking - Top of the World\\ 02 Tristam/Karma Fields/Kerli - Build the Cities (Empire of Sound)\\ 02 Arion - Blow ExXplode\\ 02 Nitro Fun - Final Boss\\ 02 Soulero - Pussycat\\ 02 Stereotronique - Sexy Beast\\ 03 Favright - Nerve\\ 03 Nitro Fun - New Game\\ 03 Tristam - Crave\\ 04 7 Minutes Dead - Delayed Friend Request\\ 04 Astronaut - Apollo (Electro Mix)\\ 04 Insan3Lik3 - Bad Pitched\\ 04 Throttle - French Kiss\\ 04 Skifonix/Stella Talpo - People Say (feat. Stella Talpo)\\ 04 Throttle - Next Big Thing\\ 05 Favright - Iceladen\\ 05 Pegboard Nerds \& Quiet Disorder - Move That Body\\ 05 Droptek - Chaos Storm\\ 05 PIXL - Astrocat\\ 05 Stereotronique - Exsoskelephone\\ 05 Astronaut/Far Too Loud - War\\ 06 Au5/Danyka Nadeau - Inside (feat. Danyka Nadeau)\\ 06 Dzeko/Torres/Crossways - TOGI\\ 06 Stephen Walking - Birthday Cake\\ 06 Insan3lik3 - Dat Voices\\ 06 Rogue - Atlantic\\ 07 Puppet/The Eden Project - The Fire\\ 07 Pegboard Nerds/Dzeko \& Torres - Bassline Kickin (Dzeko \& Torres Remix)\\ 07 Stereotronique/Northend - Rhusma\\ 07 TVDS - For You\\ 07 Stereotronique - Stock \& Pull\\ 07 Kuuro - Savage\\ 08 Case \& Point - Savage\\ 08 Noisestorm - Timewarp\\ 08 Rundfunk - A Dream\\ 09 Noisestorm - Surge\\ 09 F.O.O.L - Knight\\ 09 Stereotronique/Sebastian Ivarsson/Au5/I.Y.F.F.E/Danyka Nadeau - Tonight (feat. Danyka Nadeau) (Au5 \& I.Y.F.F.E Remix)\\ 09 Stephen Walking/Soulero - Ampersand\\ 10 Eminence - United (RedMoon Remix)\\ 10 Lets Be Friends - FTW\\ 10 Noisestorm - Airwaves\\ 10 Pierce Fulton/Puppet - Boy and the Beast\\ 10 Stereotronique - Quake\\ 11 Astronaut/Danyka Nadeau - Feronia (feat. Danyka Nadeau)\\ 11 I.Y.F.F.E - Jurassic\\ 11 Insan3Lik3/Throttle - Better Than Expected\\ 11 Stonebank - Blast from the Past\\ 13 Case \& Point - Prism\\ 13 F.O.O.L - Throne\\ 13 Stephen Walking - Dads In Space\\ 14 Favright/Cassandra Kay - Taking Over (feat. Cassandra Kay)\\ 14 Stereotronique - Gravity\\ 15 Rezonate - Pump It!\\ 15 Soulero - Aura\\ 16 Case \& Point/Gamble/Burke - All on Me (feat. Gamble \& Burke)\\ 16 Fractal - Atrium\\ 16 Varien - Resurrection of the Dagger\\ 16 Insan3Lik3 - The Other Day\\ 17 F.O.O.L - Need You\\ 17 Noisestorm - Renegade\\ 17 Razihel - Renzokuken\\ 17 Case \& Point - Error Code\\ 17 Case \& Point - Fugitive\\ 18 Astronaut - Rain\\ 18 Karma Fields - Edge of the World\\ 18 Nitro Fun - Cheat Codes\\ 18 Timmy Trumpet/SCNDL - Bleed\\ 18 Rogue - Dynamite\\ 18 Droptek - Boundaries\\ 19 Matduke - Disco Dancer\\ 19 PIXL - Sugar Rush\\ 19 Rezonate/KayoszX - Lights\\ 20 Insan3Lik3 - French Fries\\ 20 Rogue - Adventure Time\\ 20 TwoThirds/Lambert McGaughy - Skywards (feat. Lambert McGaughy)\\ 21 PIXL - The Escape\\ 21 Astronaut/Eyes/The McMash Clan - Pinball (The McMash Clan Remix)\\ 22 PIXL - This Time\\ 22 Stephen Walking - One Man Moon Band\\ 23 Case \& Point - Paradigm\\ 23 Eminence/Holly Drummond - Changes (feat. Holly Drummond)\\ 23 Skifonix - Addicted\\ 23 Stereotronique/Holly Drummond - No Holding On (feat. Holly Drummond)\\ 23 Stonebank/EMEL - Moving On (feat. EMEL)\\ 23 F.O.O.L - Keep on Rocking\\ 24 Fractal - Itvara\\ 24 Didrick - Monstercat Live Performance (3 Year Anniversary Mix)\\ 25 Fractal - Duality\\ 25 I.Y.F.F.E/Au5/Auratic - Sweet\\ 25 Pegboard Nerds - Bassline Kickin\\ 25 Stephen Walking - Porkchop Express\\ 25 Throttle - Boombox\\ 25 Unlike Pluto/Karra \& Eric Zayne - Searching For You (feat. Karra \& Eric Zayne)\\ 26 Chris Ramos/Juvon Taylor - Just Wait For It (feat. Juvon Taylor)\\ 26 Stereotronique - Grind\\ 27 Insan3Lik3 - Bliss\\ 27 PIXL - Buzz Kill\\ 27 Pegboard Nerds - Emergency\\ 27 Stonebank - The Entity\\ 28 F.O.O.L - Showdown\\ 28 Stephen Walking - It Came From Planet Earth\\ 28 Stephen Walking - The Difference Between Us and the Aliens\\ 28 Tut Tut Child - Hot Pursuit\\ 29 Noisestorm - Eclipse\\ 30 Varien - TEVA833\\
\\
 \subsection*{Progressive House}
\large Beatport Top 100 Progressive House April 2017 \normalsize\\
 00 Grum - Reflections (Original MIx)\\ 00 Kamilo Sanclemente - The White City (Original Mix)\\ 00 Marc DePulse \& Several Definitions - Birds (JOBE Remix)\\ 01 Cristoph - Eleven (Original Mix)\\ 02 Klangstof - Hostage (Sasha Remix)\\ 03 Khen - Land of Goshen (Patrice Baumel Remix)\\ 04 deadmau5 - Polaris (Original Mix)\\ 05 Cristoph - The Upside Down (Original Mix)\\ 06 Jackie Mayden - Raver Crystals (Kastis Torrau Remix)\\ 07 Jeremy Olander - Billinghurst (Original Mix)\\ 09 Marc DePulse, Rafael Cerato - Agora (Hidden Empire Remix)\\ 10 Cristoph - The Upside Down (Darker Dub)\\ 11 Sahar Z, Navar - Reality Check (Original Mix)\\ 12 Brian Cid - Pluto (Original Mix)\\ 13 Matan Caspi - Paranara (Rauschhaus Remix)\\ 14 Emi Galvan - Nothing Less (Quivver Remix)\\ 15 Quivver - Wait For You (Smash TV Remix)\\ 16 Rag And Bones - Paralyzed (Quivver Remix)\\ 17 Jeremy Olander - Damon (Original Mix)\\ 18 Juan Astudillo - Sorcerer (Original Mix)\\ 20 Matan Caspi - Paranara (Original Mix)\\ 21 Marc DePulse, Rafael Cerato - Agora (Pete Oak Remix)\\ 22 Cristian R - Dust of Fairy (Magitman Remix)\\ 23 Jerome Isma-Ae, Alastor - Kubrick (Extended Mix)\\ 24 RUFUS - Innerbloom (Sasha Remix)\\ 25 Echonomist - Nebula (Sandrino Edit)\\ 26 Bonaca - Ode to Eternal Youth (Original Mix)\\ 27 Oliver Smith - On The Moon (Spencer Brown Remix)\\ 28 Sahar Z, Navar - Bloom (Original Mix)\\ 29 Stan Kolev - Derive (Original Mix)\\ 30 Eelke Kleijn - Rubicon (Extended Mix)\\ 31 Grum - Shout (Original Mix)\\ 32 Eelke Kleijn - The Terminal (Extended Mix)\\ 33 Nocturna - Pigmental (Rick Pier O'Neil \& Desaturate Remix)\\ 34 Jerome Isma-Ae, Paul Thomas - Tomorrow (Paul Thomas \& Whit-Akre Remix)\\ 35 Roy Rosenfeld - Ahava (Original Mix)\\ 36 Solee - Morgenrotsonate (Original Mix)\\ 37 Aaryon - Ineffable Skies (Aemes Remix)\\ 38 Quivver - Mumbo Jumbo (Original Mix)\\ 39 Guy J - MDQ (Original Mix)\\ 40 Cristoph - Alone (Original Mix)\\ 41 Matan Caspi - Paranara (Kastis Torrau Remix)\\ 42 Sahar Z \& Navar - Lost in Draws\\ 43 Roger Martinez - Pan-O-Rama (Cid Inc Remix)\\ 44 Cid Inc., Darin Epsilon - Resistencia (Original Mix)\\ 45 Subconscious Tales - Focused (Original Mix)\\ 46 Guy J - Diagonal (Original Mix)\\ 47 Jeremy Olander - Panorama (Original Mix)\\ 48 Ange, Yura Popov, Yuriy From Russia - Feel The Lie (Original Mix)\\ 49 Da Luka - Chiron (Marcelo Vasami Remix)\\ 50 Peter Makto, Gregory S - Fagus (Jelly for the Babies Remix]\\ 51 Beckers, D-Nox - Mondays (Original)\\ 52 Marc DePulse, Rafael Cerato - Agora (Original Mix)\\ 53 Anii - Utopian Swept (Original Mix)\\ 54 Sandrino, Frankey - Acamar (Original Mix)\\ 55 Stan Kolev - Derive (Acid Free Dub)\\ 56 Missus - Calypso (Original Mix)\\ 57 Pryda - The End Is Just The Beginning (Original Mix)\\ 58 Yotto - Aviate (Original Mix)\\ 59 Bonaca - Deep Ocean Colours (Original Mix)\\ 60 Glenn Morrison, Elise - Mine \& Yours (Quivver Remix)\\ 61 Mearch - Orphan (Extended Mix)\\ 62 Juan Astudillo - Macumba (Original Mix)\\ 63 Mondkrater - Binary (Original Mix)\\ 64 Mønje - Submission (Original Mix) (Jiminy Hop Remix)\\ 66 Subconscious Tales - Dopa Mine (Rick Pier O'Neil Remix)\\ 67 Stan Kolev - Metanoia (Original Mix)\\ 68 Xiasou, George Ledakis - Feeling (Simos Tagias Remix)\\ 69 Inkfish - Before the War (Barry Jamieson Remix]\\ 70 Subconscious Tales - Dopa Mine (SEQU3l Remix]\\ 71 Glenn Morrison, Elise - Mine \& Yours (Jeremy Olander Remix)\\ 72 Eekkoo, Sailor \& I - Letters (Capital Jeremy Olander Remix)\\ 73 Danny Lloyd - Arapaima (Navid Mehr Remix)\\ 74 Sergio Trillini - Zeppelin (Original Club Mix)\\ 75 Mintz - In A Lonely Place (Oliver Lieb Remix)\\ 76 Antrim - It Will Be This Time (Donatello Remix)\\ 77 Pryda - Lillo (Original Mix)\\ 78 Yotto - Fire Walk (Original Mix)\\ 79 KANT - Flying Saucer (Original Mix)\\ 80 Roy Rosenfeld - Hemla (Original Mix)\\ 81 Th;en, Starkato - Sundance (Drunken Kong Remix)\\ 82 Cristoph - Cristoph (Original Mix)\\ 83 Mastrovita - Invsbl Dreams (Extended Mix)\\ 84 Stereo Underground - Glacier Meadows (Original Mix)\\ 85 Sebastien Leger - Love Star (Original Mix)\\ 86 deadmau5 - 4ware (Original Mix)\\ 87 Blood Groove \& Kikis - Harmonic (Original Mix)\\ 88 Danny Lloyd - Arapaima (Original Mix)\\ 89 Innellea - Collapse (Original Mix)\\ 90 Nick Varon - Always Forward (Marcelo Paladini Remix)\\ 91 Just Her - Follow You Down (THe WHite SHadow Remix)\\ 92 Luc Angenehm - Sendher (Simos Tagias Remix)\\ 93 Giorgia Angiuli - Now and Here (Vocal Version) (Petar Dundov Remix)\\ 94 Guy Mantzur - Blooming Fields (Original Mix)\\ 95 Da Luka - Chiron (Original Mix)\\ 96 Harper \& Green - Rejerrah (Original\\ 97 Tommer Mizrahi - Fighting For Love feat. Ilor (Brian Solis Remix)\\ 98 Lonya - Righteousness (Wally Lopez Remix)\\ 99 Jobe - Siege Of Syracuse (Original Mix) pn\\ 100 James Gill - Villa Borghese (Original Mix)\\
\end{multicols}

\huge Dataset-2 (in addition to the contents of dataset-1) \normalsize\\

\begin{multicols}{2}
 \section*{Drum \& Bass}
 \large UKF Summer Drum \& Bass \normalsize\\
 04 UKF/Dimension - Synth City\\ 06 UKF/Wilkinson - Take You Higher\\ 07 UKF/Artificial Intelligence \& Kathy Brown - Someone To Love\\ 19 UKF/Shock One - True Believer (feat. Phetsta \& Metrik)\\
 \large UKF Drum \& Bass 2015 \normalsize\\
 04 Friction - Freak (feat. Josh Barry)\\ 05 Koven - Get This Right\\ 07 Memtrix \& Spor - Darkest Hours\\ 08 Mediks - Original Selecta\\ 11 Kings of the City - Wrong (Muzzy Remix)\\
 \large UKF Drum \& Bass 2016 \normalsize\\
 08 Kove - El Camino\\ 09 The Prototypes - Transmission\\
 \large Monstercat \normalsize\\
 01 Feint/Laura Brehm - We Won't Be Alone (feat. Laura Brehm)\\ 01 Feint/Boyinaband/Veela - Time Bomb (feat. Veela)\\ 03 TwoThirds - Bring it Back\\ 03 Hot Date/Chrisson/Roufaida - To the Sun (feat. Roufaida)\\ 04 Tristam/Braken - Frame of Mind\\ 05 Muzzy - Riding The Storm\\ 06 Feint - Fury\\ 06 Feint - We Move\\ 07 Botnek/I See MONSTAS - Deeper Love\\ 09 Noisestorm - Leaving Now\\ 11 Muzzy - Children of Hell\\ 12 Hote Date/Chrisson - Overcome (This Time)\\ 12 Melano - Don't Fight It\\ 12 Melano - On Fire\\ 12 Muzzy/KG/Skyelle - Calling Out (feat. KG \& Skyelle)\\ 13 Feint/CoMa - Snake Eyes (feat. CoMa)\\ 14 WRLD - By Design\\ 14 Feint - Words (feat. Laura Brehm)\\ 15 Muzzy - Endgame\\ 17 Feint - Lonesong\\ 18 Droptek/Isabel Higuero - Killing Time (feat. Isabel Higuero)\\ 18 Muzzy/High Maintenance - The Phantom (feat. High Maintenance)\\ 18 Subformat/Charli Brix - More (feat. Charli Brix)\\ 19 Priority One/TwoThirds/Jonny Rose - Hunted (feat. Jonny Rose)\\ 19 TwoThirds/Laura Brehm - Walking Dreams (feat. Laura Brehm) (Drum \& Bass VIP Mix)\\ 20 Rameses B/Anna Yvette - Neon Rainbow (feat. Anna Yvette)\\ 24 Muzzy - Get Crazy\\ 26 Muzzy/High Maintenance - Feeling Stronger (High Maintenance Remix)\\ 27 TwoThirds - Universal\\ 29 Rameses B - Darkest Place (feat. Aloma Steele)\\ 29 TwoThirds - Origami\\
 \large UKF Bass Culture \normalsize\\
 08 Camo \& Krooked - Breezeblock\\ 36 Blu Mar Ten/InsideInfo - Still The One\\
 \large UKF Drum \& Bass 2010 \normalsize\\
 02 Nero - Electron (Nero)\\ 03 Delta Heavy - Space Time (Delta Heavy)\\ 07 Mattix \& Futile - Rising Up (Mattix \& Futile)\\ 08 Sigma/Original Sin - Front To Back (Sigma) (Original Sin Remix)\\ 09 Friction/Camo \& Krooked/Dynamite MC - Stand Up (Friction ft. C\&K \& Dynamite MC)\\ 10 Funkstar de Luxe/Metrik - Do You Feel (Funkstar de Luxe) (Metrik Remix)\\ 11 Fred V - Catch You (Fred V)\\ 12 The Blame - On My Own (The Blame) (D\&B Mix)\\ 13 L.O.A.S - Fire On Water (L.O.A.S)\\ 14 B Complex - Beautiful Lies (VIP) (B Complex)\\ 15 Crystal Fighters/Brookes Brothers - In The Summer (Crystal Fighters) (Brookes Brothers Remix)\\ 16 Shock One/Dirty Phonics - Polygon (Shock One) (Dirty Phonics Remix)\\
 \large UKF Drum \& Bass 2011 \normalsize\\
 01 Rollz - All It Took\\ 08 ShockOne - Crucify Me, Pt. 1 (feat. Phetsa)\\ 10 Friction - Someone (The Prototypes Remix) [feat. McLean]\\ 12 Shameboy - Strobot (Netsky Remix)\\ 15 Drumsound \& Bassline Smith - Close (Original Mix)\\
 \large UKF Drum \& Bass 2012 \normalsize\\
 07 UKF/Ayah Marar - The Raver (Radio Edit)\\ 09 UKF/Matrix \& Futurebound - All I Know (Smash \& Grab Mix) [feat. Luke Bingham]\\ 15 UKF/Rene LaVice - Headlock\\ 17 UKF/Mampi Swift - Gangster\\ 20 UKF/Dr Meaker - Fighter\\
 \large UKF Drum \& Bass 2013 \normalsize\\
 09 UKF/ShockOne - Lazerbeam (Ft. Metrik \& Kyza)\\ 17 UKF/Emperor - She Said\\ 19 UKF/DC Breaks - Swag\\ 20 UKF/Black Sun Empire - Arrakis (Noisia Remix)\\\\
 \\
 \subsection*{Liquid Funk}
 \large UKF Summer Drum \& Bass \normalsize\\
 01 UKF/Die \& Jenna G - 1000 Soul Songs\\ 02 UKF/Rollz - Give It Time (feat. Katies Ambition)\\ 03 UKF/Ostbahnhof \& Ugo Platana - Feel the Night (Koncept Remix)\\ 05 UKF/Fred V \& Grafix - Games People Play\\ 08 UKF/Nu:Logic - Morning Light\\ 09 UKF/Technimatic - Not Far to Go\\ 10 UKF/Lenzman - Empty Promise\\ 11 UKF/Liz-E - The Last Time\\ 12 UKF/BCee - Our Time\\ 14 UKF/Etherwood - Give It Up\\ 16 UKF/Maduk - Don't Be Afraid\\ 17 UKF/Madeon - Finale (Netsky Remix)\\
 \large UKF Drum \& Bass 2015 \normalsize\\
 06 Cartoon - Why We Lose (feat. Coleman Trapp)\\ 12 Ownglow - Change Your Life (feat. Thallie Ann Seenyen)\\ 13 Halflight - Breaking My Heart\\ 14 SpectraSoul - Shelter (feat. Lily Mckenzie) (VIP Mix) \\ 15 Dawn Wall - Between the Sheets (feat. Artificial Intelligence)\\ 16 Etherwood - Sunlight Splinters\\ 17 Calibre - Another\\ 18 Lenzman - Starz (LSB Remix) [feat. Kevin King]\\ 19 Après - Chicago (Technimatic Remix)\\ 20 Andreya Triana - Lullaby (Logistics Remix)\\
 \large UKF Drum \& Bass 2016 \normalsize\\
 01 Deadmau5 - Strobe (Dimension Remix)\\ 02 Sigma - Stay (Maduk Remix)\\ 03 1991 - Nine Clouds\\ 04 Dabin - Hold (Fred V \& Grafix Remix) (feat. Daniela Andrade)\\ 05 Brookes Brothers - Good to Me (feat. Majesty)\\ 06 DJ Friction - Dare (Hold It Down)\\ 07 Delta Heavy - White Flag VIP\\ 15 Dimension - Automatik\\ 16 High Contrast - Remind Me\\ 17 Artificial Intelligence - Shrine\\ 18 Hybrid Minds - Touch (feat. Tiffani Juno)\\ 19 Dawn Wall - I See U\\ 20 Jome - Cinnamon (Hybrid Minds Remix)\\ 21 GLXY - In Space It Never Rains (feat. Louisa Bass)\\ 22 Technimatic - Night Vision VIP\\ 23 Tritonal - Getaway (Koven Remix) (feat. Angel Taylor)\\
 \large Other liquid \normalsize\\
 00 Ed Solo/Deekline - Bam Bam (ft. Deekline)\\ 00 Konichi - Reverse Cold\\ 00 Logistics/Stella Attar - Take Me to Another World (ft. Stella Attar)\\ 00 Thomas Hayes/Kyler England - Golden (ft. Kyler England) (Original Mix)\\ 01 Brookes Brothers/Robert Owens - Beautiful (ft. Robert Owens)\\ 01 Sub Focus - Torus\\ 01 Netsky/Darrison - Escape (ft. Darrison)\\ 01 The Prototypes/Laura Vane - Taking Me Over (ft. Laura Vane)\\ 01 Sigma - Nobody to Love\\ 01 Netsky - Love Has Gone\\ 01 Wilkinson/Iman - Need To Know (ft. Iman)\\ 01 Skream/Netsky - Anticipate (ft.Sam Frank) (Netsky Remix)\\ 02 Brookes Brothers/Danny Byrd - Paperchase (ft. Danny Byrd)\\ 02 Sub Focus - Safe In Sound\\ 02 John Newman/Kove - Love Me Again (Kove Remix)\\ 02 Netsky/Dynamite MC - The Whistle Song (ft. Dynamite MC)\\ 02 Rudimental/John Newman - Feel the Love (ft. John Newman)\\ 02 Wilkinson/P Money/Arlissa - Heartbeat (ft. P Money \& Arlissa)\\
 \large UKF Bass Culture \normalsize\\
 18 Fred V - Angry Jazzer\\ 20 DJ Marky/S.P.Y. - Yellow Shoes\\ 28 KG/Genetic Bros. - Mindscape\\ 30 Rollz - Soul Caliber\\ 32 Magnus/Break - Summer's Here (Break Remix)\\ 40 Nixus - Rapture\\
 \large UKF Drum \& Bass 2010 \normalsize\\
 01 Netsky - Memory Lane (Netsky)\\ 04 Camo \& Krooked - Climax (Camo \& Krooked)\\ 05 Netsky/Shock One - I Refuse (Netsky) (Shock One Remix)\\ 06 Prototypes - Cascade (Prototypes)\\
 \large UKF Drum \& Bass 2011 \normalsize\\
 03 Bcee \& S.P.Y. - Is Anybody Out There? (Friction \& K-Tee Remix)\\ 04 Sigma - Night and Day (feat. Ikay, Foxrox \& Geetox)\\ 05 Camo \& Krooked - Shoreless\\ 07 Seba - Welcome to Our World\\ 09 Fred V \& Grafix - Long Distance\\ 11 CJ Bolland - Camargue (Fred V \& Grafix Remix)\\ 16 Heavy1 - Xiphactinus (Lenzman Remix)\\ 17 Modestep - Feel Good (The Prototypes Remix)\\ 18 The Brookes Brothers - The Big Blue\\ 19 Wilkinson - Every Time\\
 \large UKF Drum \& Bass 2012 \normalsize\\
 01 UKF/The Brookes Brothers - Loveline (feat. Haz-Mat)\\ 02 UKF/Fred V \& Grafix - Just a Thought (feat. Reija Lee)\\ 03 UKF/Rollz - Triple A\\ 04 UKF/Metrik - Freefall (feat. Reija Lee)\\ 05 UKF/The Prototypes - Suffocate\\ 06 UKF/Dimension - Digital World\\ 08 UKF/Drumsound \& Bassline Smith - Through the Night (Radio Edit) [feat. Tom Cane]\\ 10 UKF/Cyantific - Walking Away\\ 11 UKF/Sub Zero - Protection\\ 12 UKF/Total Science \& S.P.Y. - Piano Funk (feat. Riya \& DaM FunK)\\ 13 UKF/Hybrid Minds - Fade (feat. Katies Ambition)\\
 \large UKF Drum \& Bass 2013 \normalsize\\
 01 UKF/Sub Focus - Endorphins (Ft. Alex Clare) (Sub Focus vs Fred V \& Grafix Remix)\\ 02 UKF/Hamilton - You Had It\\ 03 UKF/Brookes Brothers - Carry Me On (Ft. Chrom3) (Official Video)\\ 04 UKF/John Newman -  Love Me Again (Kove Remix)\\ 05 UKF/Dimension - All I Need (Ft. Bailey Tzuke)\\ 07 UKF/Sid Batham - All Lies (Brookes Brothers Remix)\\ 08 UKF/Friction - Long Gone Memory (Ft. Arlissa)\\ 10 UKF/Kove - Searching\\ 12 UKF/Hybrid Minds - Halcyon (feat. Grimm)\\ 13 UKF/Pedestrian - Hoyle Road (Spectrasoul Remix)\\ 14 UKF/BCee - Lost \& Found (Ft. Rocky Nti)\\ 15 UKF/Ivy Lab - Afterthought (Ft. Frank Carter III)\\ 16 UKF/The Upbeats - Alone (Ft. Tasha Baxter)\\
\\
 \subsection*{Neurofunk}
 \large UKF Summer Drum \& Bass \normalsize\\
 18 UKF/Calyx, Teebee, Kemo - Pure Gold\\ 20 UKF/Friction \& Skream Ft. Scrufizzer, P Money \& Riko Dan - Kingpin (Calyx \& Teebee Remix)\\
 \large UKF Drum \& Bass 2015 \normalsize\\
 01 The Prototypes - Pop It Off (feat. Mad Hed City)\\ 02 Dimension - Whip Slap\\ 03 The Prodigy - Nasty (Spor Remix)\\ 09 Noisia \& The Upbeats - Dead Limit\\ 10 Emperor - Mind Games\\
 \large UKF Drum \& Bass 2016 \normalsize\\
 10 TC - Next Hype (Crissy Criss, Malux \& Erb n Dub Remix) (feat. Jakes)\\ 11 Spor - Mind of an Insomniac (feat. Icicle \& Linguistics)\\ 12 Phace - So Excited\\ 13 My Nu Leng \& Flava D - Soul Shake (1991 Remix)\\
 \large Other neuro \normalsize\\
 00 Ed Rush/Optical - Funktion (ft. Optical) (1X VIP)\\ 00 Flag Red - Bugspray\\ 00 Flag Red/Multi - Cataclysma (ft. Multi)\\ 00 Flag Red - Mystique\\ 00 Flag Red - Senpai\\ 01 InsideInfo/Mefjus - Pulsation\\ 01 Ivy Lab/Mefjus - Sunday Crunk (Mefjus Remix)\\ 01 Mefjus/Maksim - Change of Mind (ft. Maksim)\\ 01 The Upbeats - Beyond Reality\\ 01 Mefjus/Icicle - Contemporary (ft. Icicle)\\ 01 Spor - A1 Aztec\\ 01 Rido/Mefjus - Optimum Trajectory\\ 01 Mefjus - Blitz\\ 01 Phace/Mefjus - B\"ang B\"ang\\ 01 Flag Red - Assassins (Legacy)\\ 01 InsideInfo/Mefjus/The Upbeats - Footpath (ft. The Upbeats)\\ 01 Spor - Your Murmuring Chasms\\ 02 InsideInfo/Mefjus - Talisman\\ 02 Mefjus - Suicide Bassline\\ 02 The Upbeats/Armanni Reign - Drum Stop (ft. Armanni Reign)\\ 02 Mefjus - Dissuade\\ 02 Spor - B1 Do Not Shake\\ 02 Rido/Mefjus - Correlation\\ 02 Mefjus/Phace - Clock Off (ft. Phace)\\ 02 Phace/Noisia - Drawback\\ 02 The Prototypes - Born To Rise\\ 02 Spor - Know You\\ 02 InsideInfo/Mefjus - Leibniz\\ 02 Spor - Arms House\\ 03 Mefjus - Continuous\\ 03 The Upbeats - Diffused\\ 03 Mefjus - Leakproof\\ 03 Rido/Mefjus - Magnetism\\ 03 Mefjus - Purify\\ 03 Phace/Current Value - Wild Thing\\ 03 The Prototypes - Your Future\\ 03 Spor/Phace - Woodruff (ft. Phace)\\ 03 Spor - Always Right Never Left\\ 04 Mefjus - Emulation\\ 04 The Upbeats/Armanni Reign - Again I (ft. Armanni Reign)\\ 04 Rido/Mefjus - Causation\\ 04 Mefjus - Chaos Theory\\ 04 Phace/Rockwell - YES!\\ 04 Spor - Blurred Vision\\ 04 Spor/Hadouken! - Empire (ft. Hadouken!)\\ 05 Mefjus/Zoe Klinck - Taking (ft. Zoe Klinck)\\ 05 The Upbeats - Monogram\\ 05 Phace/Culprate - Logic Bomb\\ 05 Spor - Figaro\\ 05 Spor - Like Clockwork\\ 06 Mefjus - Saturate\\ 06 The Upbeats - One Step\\ 06 Spor - Blueroom\\ 07 Mefjus/Phace - Impuls (ft. Phace)\\ 07 The Upbeats/Trei - Thrasher (ft. Trei)\\ 07 Spor - Strange Heart\\ 08 Noisia/Calyx/Kontrol - Set me free (ft. Kontrol)\\ 08 Mefjus - Hybrid\\ 08 The Upbeats - Interval\\ 08 Spor/Tasha Baxter - As I Need You (ft. Tasha Baxter)\\ 09 Mefjus/Dope D.O.D. - Godzilla (ft. Dope D.O.D.)\\ 09 The Upbeats - Falling Into Place\\ 09 Spor - Full Colour\\ 10 Spor - If You Cry\\ 10 Mefjus - Brainwork\\ 10 The Upbeats/Tasha Baxter - Alone (ft. Tasha Baxter)\\ 11 Spor - Our Space\\ 11 Mefjus/Misanthrop - Stutter (ft. Misanthrop)\\ 11 The Upbeats - Castles\\ 12 Spor - Coconut\\ 12 Mefjus - Surrounded\\ 12 The Upbeats/Dose - Tangerine (ft. Dose)\\ 13 Spor - The Hole Where Your House Was\\ 13 Mefjus/Zoe Klinck - Blame You (ft. Zoe Klinck)\\ 13 The Upbeats - Retrograde\\ 14 Mefjus - Expedition\\ 14 The Upbeats - Undertaker\\ 16 Noisia - Dystopia (Original Mix)\\ 32 Noisia/16Bit - Machine Gun (16 Bit Remix)\\
 \large UKF Bass Culture \normalsize\\
 02 DJ Fresh - Gatekeeper\\ 29 Loadstar - Space Between\\ 37 Blokhe4d - Gutter Queen\\ 39 Futurebound/Tantrum Desire - Blind Cobblers Thumb (Tantrum Desire Remix)\\
 \large UKF Drum \& Bass 2011 \normalsize\\
 02 Noisia - Shellshock (feat. Foreign Beggars)\\ 13 A.M.C, Mattix \& Futile - The Meddler\\ 20 High Maintenence - Nowhere\\
 \large UKF Drum \& Bass 2012 \normalsize\\
 16 UKF/Calyx \& Teebee - Scavenger\\ 18 UKF/Black Sun Empire \& Noisia - Feed the Machine\\ 19 UKF/Mark Knight - Nothing Matters (Noisia Remix) [feat. Skin]\\
\\
 \section*{Dubstep}
 \large UKF Dubstep 2010 \normalsize\\
 01 Hadouken!/Gemini - Oxygen (Gemini Remix)\\ 02 Freestylers/Flux Pavilion/Belle Humble - Cracks (ft. Belle Humble) (Flux Pavilion Remix)\\ 03 Numbernin6 - Garbage\\ 04 Dubba Johnny - A Brief Introduction On Dubstep Production\\ 05 DJ Fresh/Flux Pavillion - Gold Dust (Flux Pavilion Remix)\\ 06 Nero - Innocence\\ 07 Sub Focus/Joker - Could This Be Real (Joker Remix)\\ 08 Example/Bar 9 - Kickstarts (Bar 9 Remix)\\ 09 Bar 9 - Piano Tune\\ 10 Chasing Shadows - Amirah\\ 11 Tek-One - Broken String\\ 12 Sekklow - Be Alright\\ 13 Slum Dogz - For All Time\\ 14 Dreadzone/Trolley Snatcha - Gangster (Trolley Snatcha Remix)\\ 15 B.Y.O.B./J Majik/Wickaman - Save My Life (Dubstep Mix)\\ 16 DJ Fresh - Fight\\
 \large UKF Dubstep 2011 \normalsize\\
 01 UKF/Adam F - When The Rain Is Gone (Subscape Remix) (By Adam F)\\ 02 UKF/Ayah Marar - Mind Controller (Cutline Remix) (By Ayah Marar)\\ 04 UKF/Xilent - Choose Me II (By Xilent)\\ 05 UKF/PNAU - Unite Us (Xilent Remix) (By PNAU)\\ 06 UKF/Excision \& Downlink - Existence VIP (By Excision \& Downlink)\\ 07 UKF/Flight Facilities - Crave You (Adventure Club Dubstep Remix) (By Flight Facilities)\\ 08 UKF/ShockOne - Relapse (By ShockOne feat. Sam Nafie) (Radio Edit)\\ 09 UKF/Skream - Anticipation (By Skream feat. Sam Frank)\\ 10 UKF/Example - Midnight Run (Flux Pavilion Remix) (By Example)\\ 11 UKF/Flinch - World On Fire (By Flinch)\\ 12 UKF/Oh Land - Sun Of A Gun (Jacob Plant Remix) (By Oh Land)\\ 13 UKF/Skeptiks - Cobwebs (By Skeptiks)\\ 14 UKF/Flux Pavilion - I Can't Stop (By Flux Pavilion)\\ 15 UKF/Flux Pavilion - Bass Cannon (By Flux Pavilion)\\ 16 UKF/Foxes - Youth (Adventure Club Dubstep Remix) (By Foxes)\\ 17 UKF/Gemini - Graduation (By Gemini)\\ 18 UKF/Juggernaut Bitch - Juggernaut Bitch (Noire)\\ 19 UKF/Studio Killers - Ode To The Bouncer (Xilent Remix) (By Studio Killers)\\ 20 UKF/Sub Focus - Falling Down (feat. Kenzie May) (By Sub Focus)\\ 21 UKF/Krome \& Time - The License (Doctor P Remix) (By Krome \& Time)\\
 \large UKF Dubstep 2012 \normalsize\\
 01 UKF/Emalkay - Bring It Down\\ 02 UKF/Zeds Dead - Adrenaline\\ 03 UKF/xKore - Stabs\\ 04 UKF/Feed Me \& Gemini - Whiskers\\ 06 UKF/Tritonal - Still With Me (feat. Cristina Soto) [Seven Lions Remix]\\ 07 UKF/Xilent - Universe (feat. Shaz Sparks)\\ 08 UKF/Zomboy - City 2 City (feat. Belle Humble)\\ 09 UKF/Ayah Marar - The Raver (Xilent Remix)\\ 10 UKF/The Prototypes - Suffocate (Koven Remix)\\ 11 UKF/Dubba Jonny - Always\\ 12 UKF/Laxx - You Turn Me\\ 13 UKF/Snarebox - Bounce\\ 14 UKF/Taiki \& Nulight - Rising Up\\ 15 UKF/Netsky - Wanna Die For You (feat. Diane Charlemagne)\\ 16 UKF/Borgore - Decisions (Original Mix)\\ 17 UKF/Eptic - Like a Boss\\ 18 UKF/Excision - Sleepless (feat. Savvy) [Xilent Remix]\\ 19 UKF/KillSonik - Bloodlust\\ 20 UKF/Skism - Experts\\
 \large UKF Dubstep 2013 \normalsize\\
 01 UKF/Flux Pavilion - Gold Love (feat Rosie Oddie)\\ 02 UKF/Krewella - Live For The Night (Pegboard Nerds remix)\\ 03 UKF/Ellie Goulding - Explosions (Gemini remix)\\ 04 UKF/Sub Focus - Endorphins (feat Alex Clare)\\ 05 UKF/Feed Me \& Tasha Baxter - Ebb \& Flow\\ 06 UKF/Datsik - Hold It Down (feat Georgia Murray)\\ 07 UKF/Torqux - T1\\ 08 UKF/Culprate - Scarred\\ 09 UKF/Emalkay - The Line (feat Glen Boden)\\ 10 UKF/Au5 - Metronic\\ 11 UKF/Zomboy - Mind Control\\ 12 UKF/KATFYR - Binary\\ 13 UKF/501 - The Final Cut\\ 14 UKF/AWE - Jurassic\\ 15 UKF/Tristam - Truth (Candyland remix)\\ 16 UKF/Rollz - Burn Up (feat Katie's Ambition - Dabin remix)\\ 17 UKF/Subscape - I Need You\\ 18 UKF/Juventa - Move Into Light (feat Erica Curran - Koven remix)\\ 19 UKF/Koven - More Than You\\ 20 UKF/Xilent - Boss Wave\\ 21 UKF/Mojo - Blues\\ 22 UKF/KOAN Sound \& Asa - Tetsuo's Redemption\\
 \large Others \normalsize\\
 01 Klaypex/KATFYR - Let It Go (ft. KATFYR)\\ 02 Klaypex/Ellie Goulding - When I'm Alone (Klaypex Remix)\\ 03 Klaypex/Deadmau5 - Strobe (Klaypex Remix)\\ 04 Klaypex/Rihanna - We Found Love (Klaypex Remix)\\
 \large UKF Bass Culture \normalsize\\
 01 Foreign Beggars/Skrillex - Still Getting It (ft. Skrillex)\\ 04 Gemini - Elevate\\ 05 Excision/Downlink/Skism - Heavy Artillery (Skism Remix)\\ 06 Cutline - Alive\\ 07 Feed Me/Tasha Baxter - Strange Behaviour (ft. Tasha Baxter)\\ 11 16Bit - Frzr9000\\ 12 The Prototypes/Cutline - Cascade (Cutline Remix)\\ 13 J Majik \& Wickaman - Assassin\\ 15 K.O.A.N Sound - Trouble In The West\\ 19 Dubba Jonny - What Have You Got\\ 21 Datsik/Levella - Firepower (Levella Remix)\\ 22 Dodge \& Fuski - Aerophobia\\ 23 Engine-Earz Experiment - They Live\\ 24 Camo \& Krooked/Shaz Sparks - All Fall Down (ft. Shaz Sparks)\\ 26 Spor/Chasing Shadows - Pacifica (Chasing Shadows Remix)\\ 27 Foreign Beggars/Trolley Snatcha/Noisia - Contact (Trolley Snatcha Remix) (ft. Noisia)\\ 31 Roksonix/Statelapse - Let's Go\\ 34 Interface/Shahin Bader - Twister (ft. Shahin Bader)\\ 35 Dodge \& Fuski - Come Again\\
\\
\section*{House}
\subsection*{Deep House}
 \subsubsection*{Future House}
 \large Beatport Top 100 Future House May 2017 \normalsize\\
 00 Chocolate Puma \& Bart B More - Rising Up (Extended Mix)\\ 00 EDX - Feel The Rush (Original Club Mix)\\ 00 Throttle - Found You (Make Me Yours) (Extended Mix)\\ 00 Coldplay, The Chainsmokers  - Something Just Like This (Don Diablo Remix)\\ 00 Mike Williams, Brezy - Don't Hurt feat. Brezy (Extended Mix)\\ 00 Mr.Belt \& Wezol - Good Times (Extended Mix)\\ 00 Merk \& Kremont, Kris Kiss - GANG feat. Kris Kiss (Original Mix)\\ 00 Pep \& Rash, D-Double - Break Down feat. D-Double (Extended Mix)\\ 00 Watermat, Kelli-Leigh - Won't Stop feat. Kelli-Leigh (Bob Sinclar \& The Cube Guys Extended Remix)\\ 00 Chris Lake - I Want You\\ 00 Jay Hardway - Golden Pineapple (Original Mix)\\ 00 Funkin Matt - Aurora (Extended Mix) \\ 00 Calippo -  We'll Be Heard (Original Mix)\\ 00 Throttle  -  Hit The Road Jack (Cazztek Remix)\\ 00 Zonderling - Tunnel Vision (Don Diablo Extended Edit)\\ 00 Yves V \& Marc Benjamin - Blow (Extended Mix)\\ 00 D.O.D. - Sixes (Clean) (Extended)\\ 00 Sagan \& Plastik Funk - Got No Love (Extended Mix)\\ 00 HAEVN - Finding Out More (EDX'S Acapulco At Night Extended Remix)\\ 00 Bakermat - Baby (Extended Mix)\\ 00 Martin Garrix, Brooks - Byte (Original Mix) Clean\\ 00 Stadiumx feat. BISHÃP -  The Fall (Extended Mix)\\ 00 Throttle - Hit The Road Jack (Extended Mix)  \\ 00 Pandaboyz \& Nano Bites - Mumble (Extended Mix)\\ 00 Loge21 - Need U (feat. Dee Ajayi) (Original Mix)\\ 00 Mesto, Curbi - BRUH (Extended Mix)\\ 00 Don Diablo \& Marnik - Children Of A Miracle (Don Diablo VIP Remix)\\ 00 Lucas \& Steve, Pep \& Rash - Feel Alive\\ 00 HI-LO - The Answer (Oliver Heldens Extended Edit)\\ 00 Alok \& Bruno Martini feat. Zeeba - Hear Me Now (EDX \& Nora En Pure Remix)\\ 00 Tchami - Adieu (Clean) (Extended)\\ 00 Loge21 - Just Bass\\ 00 Tommy Trash + DENM - Dreamer (Extended Mix)\\ 00 TRU Concept \& Nu Aspect -  Said To You (Original Mix)\\ 00 Tujamo - Make U Love Me (Extended Mix)\\ 00 Lika Morgan - Feel The Same (EDX Dubai Skyline Remix)\\ 00 Dillon Nathaniel - Funk With Us (Original Mix)\\ 00 Sander Van Doorn, HI-LO - WTF (Extended Mix)\\ 00 Mark Johns - HOT DRUM (Original Mix)\\ 00 Moby, Brohug - Natural Blues (Extended Mix)\\ 00 Don Diablo - Cutting Shapes (Extended Mix)\\ 00 Just Kiddin - More To Life (Extended Mix)\\ 00 Stadiumx \& Muzzaik  -  Last Night A D.J. Saved My Life (Extended Mix)\\ 00 Luca Debonaire - Walking on Clouds (Croatia Squad Remix\\ 00 Phlegmatic Dogs - Keepmastik (Original Mix)\\ 00 Croatia Squad - Make You Hustle (Original Club Mix)\\ 00 Lucas \& Steve, Wulf, Sam Feldt - Summer on You (Club Edit) feat. Wulf (Club Mix)\\ 00 Aloe Blacc, Aeroplane, Purple Disco Machine - Counting On Me feat. Aloe Blacc (Extended Mix)\\ 00 DJ Snake, Justin Bieber - Let Me Love You (Don Diablo Remix)\\ 00 La Fuente - Capitol (Extended Mix)\\ 00 Angelz - Devils (Cazztek Remix)\\ 00 Cash Cash \& ROZES - Matches (Holl \& Rush Remix)\\ 00 Paige - West Coast Party (Clean)\\ 00 Croatia Squad,Lika Morgan - Make Your Move (Original Mix)\\ 00 Noizu - Lasers\\ 00 Birdy - Keeping Your Head Up (Don Diablo Remix)\\ 00 Cedric Gervais, Digital Farm Animals, Dallas Austin - Touch The Sky (Extended\\ 00 Mark Villa \& Keanu Silva feat. F51 - Lots To Say (Keanu Silva VIP Mix)\\ 00 Dirtyloud - Heartbeat (Original Club Mix)\\ 00 Tony Quattro - Fuerza (feat. Nani Castle)\\ 00 Chris Lake - Operator (Ring Ring) ft. Dances With White Girls (Extended Mix)\\ 00 Oliver Heldens - I Don't Wanna Go Home (Kyle Watson Remix)\\ 00 Chocolate Puma, Pep \& Rash - The Stars Are Mine (Extended Mix)\\ 00 Bingo Players - Cry (Just A Little) (A-Trak and Phantoms Remix)\\ 00 Robby East \& Robbie Mendez - Heartfelt (Extended Mix)\\ 00 Dillon Nathaniel - Frequent (Original Mix)\\ 00 Malaa - Bylina\\ 00 Destructo \& VOLAC - What I Got (Dirty) (Extended)\\ 00 Tchami - SIAW (Original Mix)\\ 00 Mr. Belt \& Wezol - Boogie Wonderland (Extended Mix)\\ 00 Jauz - Feel The Volume (JOYRYDE 'Stick It In Reverse' Mix)\\ 00 Martin Solveig \& Gta - Intoxicated (Original Mix)\\ 00 Vato Gonzalez - Bassline Riddim (Extended Mix)\\ 00 Funkerman \& Cooperated Souls - Bad Boy Beat (Extended Mix)\\ 00 RetroVision -  Up \& Down (Original Mix)\\ 00 Lucas \& Steve - Love On My Mind (Extended Mix)\\ 00 Martin Solveig feat. Ina Wroldsen - Places (Club Mix)\\ 00 Lucas \& Steve, Jake Reese - Calling On You feat. Jake Reese (Club Mix)\\ 00 Malaa - Notorious (Original Mix)\\ 00 Earth, Wind \& Fire, Throttle - September\\ 00 QUIX - Deep Home\\ 00 Ralvero \& Redhead Roman - Bubblegum (Original Mix)\\ 00 Dance Cult, TIAAN - Danger (Original Mix)\\ 00 Laidback Luke \& Made In June - Paradise (Featuring Bright Lights) (Extended Mix)\\ 00 Tom \& Jame Vs. Holl \& Rush - Move On Me (Extended Mix)\\ 00 Don Diablo - Switch (Extended Mix)\\ 00 Brohug X Moby - Natural Blues (Dub Extended Mix)\\ 00 PBH \& Jack Shizzle x The Time Frequency Ft. Tahira Jumah  -  Higher (Extended Mix)\\ 00 Ephwurd - Vibrations (Extended Mix)\\ 00 Malaa - Diamonds (Brohug Remix) (Original Mix)\\ 00 Nora En Pure - On the Beach (Original Mix)\\ 00 Caitlin Stubbs, The City Never Sleeps - The Feeling (Original Mix)\\ 00 Axwell And Ingrosso Ft Kid Ink - I Love You (CID Remix) (Extended) (Clean)\\ 00 Martin Garrix, Dua Lipa - Scared To Be Lonely (Brooks Remix)\\ 00 Sam Feldt - Show Me Love (Edx's Indian Summer Remix)\\ 00 Tom Staar, Rob \& Jack - Sunshine (Extended Mix)\\ 00 Angelz - Devils (VOLAC Remix)\\ 00 Tony Romera - What s Going On (Original Mix)\\ 00 Volac - Shit Man (Original Mix)\\ 00 Aevion - Summer (Original Mix) \\
 \large Monstercat Bass House \normalsize\\
 02 Jauz/Pegboard Nerds - Get On Up\\ 07 Tokyo Machine - PARTY\\ 07 Rootkit - Strung Out\\ 08 Stonebank - Droppin' Low\\ 09 Stonebank - Lost Without You\\ 21 Topi - Swapping Things\\ 22 Rootkit - Good 2 Go (feat. Tylor Maurer)\\ 23 Rootkit - Levitate (feat. Tylor Maurer)\\ 23 Tokyo Machine - OKAY\\ 23 PIXL/Pairanoid - Bring It\\ 27 Tokyo Machine - Crazy\\ 27 Candyland \& Ricci - Touch Me\\
 \large Monstercat Future House \normalsize\\
 01 Haywyre - Do You Don't You\\ 02 Vicetone - Nevada (feat. Cozi Zuehlsdorff)\\ 04 Varien/Veela - Supercell (feat. Veela)\\ 05 Au5/Danyka Nadeau - Follow You (feat. Danyka Nadeau)\\ 06 Rootkit/Danyka Nadeau - Real Love (feat. Danyka Nadeau)\\ 08 Tut Tut Child - I Can't\\ 09 Mr FijiWiji/Meron Ryan - Believe Her (feat. Meron Ryan)\\ 11 Mr FijiWiji/Direct - Entropy\\ 13 Mr FijiWiji - Let Me Out\\ 14 Laszlo - Messiah\\ 15 Laszlo - Sphere\\ 22 Rootkit - Elevate\\ 25 GLACIER - Neos\\ 26 Laszlo - Airglow\\ 27 PIXL/Q'AILA - Here For You (feat. Q'AILA)\\ 30 Mr FijiWiji/Jonny Rose - Out on a Limb (feat. Jonny Rose)\\ 30 Stonebank - Back to Start (feat. Dylan Dunlap)\\
\\

\section*{Hip Hop}
\subsection*{Chillhop}
 \large Others \normalsize\\
 01 Jinsang - bright.\\ 01 Freddie Joachim - Moments\\ 02 Jinsang - morning.\\ 02 Freddie Joachim - One Foot Forward\\ 03 Jinsang - pine leaves.\\ 03 Freddie Joachim - Autumn Rain\\
\subsection*{Trap}
 \subsubsection*{Future Bass}
 \large [2016] - Agari Vol. 005 \normalsize\\
 01 Filip - I Know\\ 02 Erik Soto/Croix - Kinder (ft. Croix)\\ 03 Madnap \& Holly - Hidden Paradise\\ 04 Leotrix - Shook Up\\ 05 Jon Prezant \& VDG - Remember Me\\ 06 Acaer - U\\ 07 Maytek - Fire\\ 09 Sadkey - Further\\ 10 DSFGR/Tara Louise - Soulmate (ft. Tara Louise)\\ 11 Shisto \& James Gent - Jada\\ 12 Inverness \& So Sus - Infinite Soju\\
 \large Ministry Of Sound - Future Bass 2015-WEB (2015) \normalsize\\
 01 Sam Smith - Like I Can (Jonas Rathsman Remix)\\ 02 Caribou - Your Love Will Set You Free (C2's Set U Free RMX)\\ 03 Kaytranada - Leave Me Alone\\ 04 George Maple - Talk Talk (Moon Boots Remix)\\ 05 Krystal Klear - One Night Only (Low Steppa Remix)\\ 06 Dusky - Yoohoo (Benton Remix)\\ 07 Hannah Wants - Rhymes (Sonny Fodera Remix)\\ 08 DJ Fresh - Gravity (Roska Remix)\\ 09 Jessie Ware - Champagne Kisses (TCTS Remix)\\ 10 Kokiri - Retrospect (Illyus \& Barrientos Remix)\\ 11 Karen Harding - Say Something (Bodhi Remix)\\ 12 Cyril Hahn - Perfect Form\\ 13 Shiba San - Kick Your Ass\\ 14 Roska - Higher\\ 15 Waze \& Odyssey - Ways Of The Underground\\ 16 Little By Little - Bang The Box\\ 17 Stonebridge - Put 'em High (Atilla Cetin Nitec Remix)\\ 18 Sandy Rivera - Physical\\ 19 My Digital Enemy - Got To Have U\\ 20 EDX - Want You (Radio Edit)\\ 21 Whilk - Darklands (Kidnap Kid Remix)\\ 22 Billy Kenny - Lights\\ 23 Gregori Klosman - Red Lights\\ 24 The Dealer - For A Night (Panda Remix)\\ 25 Beckwith - Words I Got\\ 26 Meditate - What You Do (Jade Blue Remix)\\ 28 Jason Burns - Lightweight (Sandy Rivera Remix)\\ 29 Jessie Ware - You \& I (Forever) (Shift K3Y Remix)\\ 30 Jack Garratt - The Love You've Given\\
 \large Monstercat Future Bass \normalsize\\
 01 Grant Bowtie - Reach\\ 01 San Holo/Tessa Douwstra - Hold Fast (feat. Tessa Douwstra)\\ 02 Seven Lions \& Echos - Cold Skin\\ 04 Kasbo - Kaleidoscope\\ 05 Anevo - Don't Shoot Me Down (feat. Jae-Mi)\\ 06 Conro - I Wanna Know\\ 06 Savoy/Sound Remedy/Jojee - Leaving You (feat. Jojee)\\ 06 Conro/Royal - City Lights (feat. Royal)\\ 06 Anevo - Feel Something (feat. Kayla Diamond)\\ 07 Grant Bowtie - Clockwork\\ 07 WRLD/Richard Caddock - Orbit (feat. Richard Caddock)\\ 07 Pegboard Nerds - Emoji\\ 07 San Holo/The Nicholas - They Just Haven't Seen It (feat. The Nicholas)\\ 08 Grant - Wake Up (feat. Jessi Mason)\\ 08 Grant - Starship\\ 09 Tokyo Machine - Blast\\ 09 Conro - On My Way Up\\ 09 Hellberg - The Girl (Color Source Remix)\\ 09 WRLD - Triumph\\ 10 MYRNE - Afterdark (feat. Aviella)\\ 10 Kasbo - Again\\ 11 Grant Bowtie - High Tide\\ 11 Haywyre - I Am You\\ 11 Snavs - Time\\ 11 Grant - Constellations (feat. Jessi Mason)\\ 12 Deon Custom - Aloha\\ 14 Hush/All About She - Fopspeen (Bound 2 U) [feat. All About She]\\ 14 Dirty Audio \& Max Styler - Roller Coaster\\ 16 Grant Bowtie - Cloud Nine\\ 16 San Holo - Victory\\ 17 Richard Caddock/Hyper Potions - Distance\\ 17 Hyper Potions - Porta Vista\\ 18 SMLE - Halo (feat. Helen Tess)\\ 19 Stephen Walking/Hyper Potions - Saturday Morning Space Ride\\ 19 Subtact - Tunnel Vision\\ 20 Rich Edwards - For You (feat. Park Avenue)\\ 20 Deon Custom - Roses\\ 20 San Holo - New Sky\\ 20 Savoy/Chali 2na - Love Is Killing Me (feat. Chali 2na)\\ 20 Hush - Pilvorm\\ 21 Subtact - Restart\\ 21 Soupandreas \& Inverness - Tumbling Down\\ 22 Stephen Walking - Hey\\ 23 Summer Was Fun - My Dear\\ 24 Laszlo/WRLD - You \& Me\\ 24 Soupandreas - Over You\\ 25 Aero Chord - The 90s\\ 25 Richard Caddock - Glow\\ 26 Deon Custom - Together\\ 27 Astronaut/Harry Brooks Jr./WRLD - Champions (WRLD Remix) (feat. Harry Brooks Jnr)\\ 28 Hyper Potions/Subtact - Adventures\\ 29 Conro - The Saint\\ 30 Sushi Killer/Kevin Villecco - Anime Bae\\
 \large Monstercat Trap \normalsize\\
 02 Marshmello - Alone\\ 03 Unlike Pluto - Found You (feat. Michelle Buzz)\\ 05 Rogue - Ultimatum\\ 10 Candyland \& Shoffy - Faces\\ 11 Anevo - Waiting on Your Call (feat. Park Avenue)\\ 29 Varien/Charlotte Haining - Hypnotique (feat. Charlotte Haining)\\
 \large Trap \normalsize\\
 00 Alessia Cara/Lucian - Here (Lucian Remix)\\ 00  - TRNDSTTR\\ 00  - Me \& You\\ 00  - Really\\ 00 Panama/Wave Racer - Always (Wave Racer Remix)\\ 00 San Holo/Yellow Claw - Alright (ft. Yellow Claw)\\ 01 Area21 - Spaceships\\ 01 Laxo  - Popsicles With Friends\\ 01 Mike Diva - Our Glorious Leader\\ 01 Snail's House - Grape Soda\\ 01 Snail's House - Ma Couchoute\\ 01 Wave Racer/Cosmo's Midnight - Introooo (ft. Cosmo's Midnight)\\ 02 Deon Custom - Bliss (Original Mix)\\ 02 Wave Racer/Lido - World Record (ft. Lido)\\ 03 Deon Custom - Circles (Original Mix)\\ 03 Wave Racer/B?by - Flash Drive (ft. B?by)\\ 04 Deon Custom - Feathers (Original Mix)\\ 04 Wave Racer - Bubble Wrap\\
 \large Trap Nation Top 20 \normalsize\\
 00 Dr. Dre - The Next Episode (feat. Snoop Dogg)\\ 00 Fetty Wap - Trap Queen\\ 00 Jetta - I'd Love to Change the World\\ 00  - Vanic x K.Flay - Can"t Sleep\\
 \large VA - Best of Trap Music [2014] \normalsize\\
 48 Zedd - Follow You Down (feat. Bright Lights) (Keys N Krates Remix)\\
\\
\section*{Hard Dance}
 \subsection*{Happy Hardcore}
 \large VA - Happy Hardcore 1-2CD-1995-exp \normalsize\\
 01 Critical Mass - Dancin' Together\\ 01 DJ Wierdo \& DJ Sim - Go Get Busy (Extended Rave Version)\\ 02 DJ Paul - Pump This Party\\ 02 The Prophet - I Love You\\ 03 Scooter - Move Your Ass\\ 03 DJ Paul - Life Is Like A Dance\\ 04 D'ohm Feat. Tofke \& Insider - Mushrooms\\ 04 Infectious - I Need Your Lovin'\\ 05 Force Mass Motion - The Deep\\ 05 Rave Lab - Seeing Is Believing\\ 06 Rod-Yler Feat. Clinique Team - Mission Fulfilled\\ 06 Protect System - Waves Of Energy\\ 07 Eurocore - Right To Rythm\\ 07 Interactive - Forever Young\\ 08 Scott Brown Meets DJ Paul - Feel The Music\\ 08 Jimmy J \& Cru-l-t - Six Days\\ 09 Undercover Anarchist feat. Juggenaut - Rave Nation\\ 09 Alien Factory - Tomorrow (Remix)\\ 10 Brothers In Crime - Dance (Charly Lownoise Remix)\\ 10 Dr.Phil Omanski - Feeling\\ 11 Emmanuel Top - Fly Fox\\ 11 Wasteland - Live\\ 12 Active Force - Head Like A Pacman\\ 12 Goldilox - You Are My Sunshine\\ 13 DJ Sim - Happy Organ\\ 13 Ultimate Seduction - Togheter Forever\\ 14 Simon C - Fuck You\\ 14 Ultrasonic - Check Your Head\\ 15 T-Scanner - Trip To Heaven\\ 15 The Prophet - Allright Now Here We Go (DJ Rob Mix)\\ 16 Toni Salmonelli - L.O.V.E.\\ 16 Terra W.A.N. - Puta Madre '95 (T.N.T. Remix)\\
 \large VA - Happy Hardcore 2-2CD-1995-exp \normalsize\\
 01 Technohead - I Wanna Be A Hippy\\ 01 Scott Brown - Do What You Like (The Rezerection Anthem)\\ 02 DJ Paul Elstak - Luv U More\\ 02 Micado - It's Gonna Be A Fine Night\\ 03 Dune - Hardcore Vibes\\ 03 Network - Words\\ 04 DJ Waxweasle - Come With Me\\ 04 Bertocucci Feranzano \& DJ Buzz Fuzz - Higher Love\\ 05 Mindcontrollers - Sweet Dreams (Nightmare Mix)\\ 05 Scorpia (La Central Del Sonida) - Hypnose\\ 06 Dyewitness - Masterplan\\ 06 System Shock - Bizzy Time\\ 07 M-Jay \& Dan Vee - The Sun Always Shines\\ 07 Mr Kinky - Just Laugh\\ 08 Rave Nation - Going Crazy\\ 08 Highlander - Hold Me Now (Bass D \& King Matthew Remix)\\ 09 The Prophet - Big Boys Don't Cry (Rave Mix)\\ 09 Bill Daniel Bunter \& JDS Feat Gem - Let It Lift You (DJ Vibes \& Wishdokta Mix)\\ 10 Hyperactive - Who Is Elvis\\ 10 Full Option - Rave All Night\\ 11 Bertocucci Feranzano - Sax B 4 Diner\\ 11 Happy Toons - I Want You\\ 12 DJ Weirdo \& DJ Sim - Pump That Stupid Bass (Happy Rave Mix)\\ 12 Ramirez - Baraonda\\ 13 DJ Delirium - Be Happy!\\ 13 Forbes \& Cyclone - Full Forcer\\ 14 Too Fast For Mellow - Get My Love\\ 14 DJ Vibes \& Wishdokta - Hardcore Business\\ 15 Tim B - Can You Feel It\\ 15 Critical Mass - Dancing Together\\ 16 The Beatfreaks - Miles Of Smiles\\ 16 Tony Salmonelli - Hey! (buzzy's Ragga Mix)\\
 \large VA - Happy Hardcore 3-2CD-1995-exp \normalsize\\
 01 Club X - The Sequel (La La La)\\ 01 2 Brothers On The 4th Floor - Come Take My Hand (K\&A's Extended Rave Blast)\\ 02 DJ Paul Elstak - Rainbow In The Sky\\ 02 T.N.T. - Let's Get Together (Radio Mix)\\ 03 Critical Mass - Burnin' Love (Original Version)\\ 03 Ravers World - Paradise Of Rave\\ 04 No Velocity - Right Here\\ 04 Planoforce - Listen To Me\\ 05 Los Pablos - It's A Dream (Short Dream Mix)\\ 05 Jayke - Summertime Rave\\ 06 Citadel Of Kaos feat. Buzz Fuzz - Show Me Love\\ 06 Cherrish - Happy Friday\\ 07 Nina Feranzano \& Buzz Fuzz - Keep It Up\\ 07 Sonic Driver - In Your Arms Tonight\\ 08 T.O.T.T - Get It Up (Airplay Edit)\\ 08 Alk-E-D - Home (Luna C Remix)\\ 09 Wicked Dimension - Everytime I Think Of You\\ 09 The Prophet \& Delirium - The Way You Make Me\\ 10 Ferocious - Please Don't Go\\ 10 DJ Waxweazle - Techno Hits Ya\\ 11 CIXX - Ride The Rhythm (Radio Mix)\\ 11 Bass D \& King Matthew - Take Me Higher (Gizmo Remix)\\ 12 Rave Religion - C'mon And Touch Me\\ 12 The Insaniacs - Full Of Music\\ 13 Bertocucci Feranzano - XTC Love (Radio Mix 1)\\ 13 Seduction \& Eruption - Bust The New Jam\\ 14 D-Jumpmaster - Dance To Da Bells\\ 14 Public Domain - Get Stupid\\ 15 The Prophet \& DJ Delirium - Breakdown\\ 15 UK - Heaven\\ 16 3 Steaps Ahead - Drop It (Happy Mix)\\ 16 Buzz Fuzz - Freedom\\
 \large VA - Happy Hardcore 4-2CD-1996-exp \normalsize\\
 01 Party Animals - Have You Ever Been Mellow\\ 01 Critical Mass - Burnin' Love\\ 02 DJ Paul Elstak - Don't Leave Me Alone\\ 02 Brothers In Crime - Forever\\ 03 Love Decade - See Me Jumping\\ 03 Mindtrust - Ravers Groove\\ 04 Dominion - Salted Popcorn\\ 04 The Beatsquad - Miles Of Smiles\\ 05 DJ Omar Santana - Time To Motivate (Happy Mix)\\ 05 Billy Bunter \& D-Zyne - Ride Like The Wind\\ 06 Cherrish - Burning Up\\ 06 No Velocity - Give Me Body\\ 07 Elips - Don't Try\\ 07 Pulp Shock - Take Me Away\\ 08 Pulp Shock - Far Away\\ 08 DJ Weirdo \& DJ Sim - Pump That Stupid Bass (Radio Mix)\\ 09 Rob's Project - Loving You\\ 09 DJ Lingo \& The Skycat - Together Forever\\ 10 Q-Tex - Can't Get Enough\\ 10 Erption feat. Katherine Wood - Let The Music\\ 11 DJ Promo - Sing It Louder (Sirekit Mix)\\ 11 Smile - Movin\\ 12 Profound - 4 O'Clock\\ 12 Lords Of The Underground - Making Moves\\ 13 Creasemaster \& Slamdog - Bump The Bass\\ 13 DJ E-Rick \& Tactic - Hysterical Drumbeats (Original Mix)\\ 14 Dougal \& Eruption - Partytime\\ 14 DJ Waxweazle \& DJ Delirium - Dreams Of Heaven\\ 15 Cixx - Clap Your Hands\\ 15 DJ Rob \& Tim B - Touch The Sky\\ 16 Big Deal - The Right Place\\ 16 Carlos Masserati - Get On The Move (Happy Mix)\\
 \large VA - Happy Hardcore 5-2CD-1996-exp \normalsize\\
 01 Party Animals - Hava Naquila (Flamman \& Abraxas Radio Mix)\\ 01 Critical Mass - Believe In The Future\\ 02 DJ Paul Estak - The Promised Land\\ 02 Lipstick - Queen Of The Rhythm\\ 03 Mindtrust - Ravers Groove\\ 03 Wonderland - Be On A Star\\ 04 Dr Phil Omanski - Let It (Short Hard Disco Mix)\\ 04 Q-Tex - Trip To The Hyperdome\\ 05 No Velocity - Here We Go (Playing The House)\\ 05 Lexus Lovers - Beat Of The Bass\\ 06 Discofrisco \& DJ Inferno - Give All Your Love\\ 06 Solid Bass - The Girl Of Dreams\\ 07 DJ Dougal \& Mickey Skeedale - Emerald\\ 07 Phaze 2 Phaze Meets The Doctor - Tales From The Crypt\\ 08 3 Steps Ahead - Drop It (Happy Mix)\\ 08 Hocus Pocus - Here's Johnny\\ 09 2 Brothers On The 4th Floor - Fairytales (Charly Lownoise \& Mental Theo)\\ 09 OHM - Trip To Paradise\\ 10 Jayke - Wish Come True (Extended Version)\\ 10 Revolution Team - Makin' Up Your Mind\\ 11 Bueno - Liberty\\ 11 James Daltan - Touch Me\\ 12 Fiction Factory - Don't Make Me Cry\\ 12 Commotion - Stick It In\\ 13 DJ Fury - All I Ever Wanted\\ 13 Bertocucci Feranzano \& Toni Salmonelli - Daddy Snow\\ 14 Nina Feranzano \& Buzz Fuzz - Keep It Up (Radio Mix)\\ 14 Cixx - Ride To The Rhythm\\ 15 Mac Project - Everybody (Hard)\\ 15 Global Split - Power I Want Some\\ 16 DJ Vibes \& Wishdokta - Givin' It All I Got\\ 16 Angel - Take Me Away\\ 17 T-Bass \& Centigrade - Walk Of Life\\ 17 DJ Weirdo \& Dr Phil Omanski - Young Birds\\
 \large VA - Happy Hardcore 6-2CD-1996-exp \normalsize\\
 01 Critical Mass - Believe In The Future\\ 01 Technohead - Happy Birthday\\ 02 Nakatomi - Children Of The Night\\ 02 Dionysis - Break On Through\\ 03 4 Tune Fairytales - My Little Fantasy\\ 03 The Nightraver \& DJ Trevor - The Revolution\\ 04 Mr. B - Love Fantasy\\ 04 No Velocity - 31 Seconds Of Your Time\\ 05 JDS - Higher Love\\ 05 The Prophet - Can't Stand It\\ 06 Trancehistory - Doo Dey\\ 06 Ikon ft. Elaine - Doesn't Have To Be\\ 07 Justin Time - Help Me\\ 07 The Beatsquad - The Beat Goes On\\ 08 Happymen - Love Is You\\ 08 External - Circles\\ 09 Tiny Tot - Discoland\\ 09 Human Resource - Dominator '96\\ 10 Cherrish - Journey Through The Night\\ 10 Back 2 Bass - I Wanna Be With You\\ 11 Lovelife - Hold Me\\ 11 Clear The Air - MC Drokz\\ 12 James Daltan - Strangers\\ 12 Highlander - Open Your Eyes\\ 13 Lords of the Underworld - For The People\\ 13 Cixx - Gimme Da Pope\\ 14 T-Marc ft. Vincent \& Cleon - One Two\\ 14 Solid Base - Can't Stop\\ 15 The Beatsquad - Uptempo Beatz\\ 15 The Propher \& Slamdog - Vicious Beat\\ 16 Skorpus Ravers vs. Cyntex - Bombdebomb\\ 16 DJ Delirium - Rock Your Body\\
 \large VA - Happy Hardcore 7-2CD-1996-exp \normalsize\\
 01 Blue Zone - Too Beautiful (Cixx's Happy Hardcore Remix)\\ 01 Brothers in Crime - Destiny ([DJ Norman Mix)\\ 02 Active Force - Breakdown on The Floor\\ 02 Ultimate Buzz ft. MC Bee - Live 'N Direct\\ 03 Helix Featuring Marlon \& Becks - U R Everything\\ 03 DJ Isaac - I Wanna Be a Gabber Baby\\ 04 DJ Promo - Into The Light\\ 04 Firefax \& Firebird - Movin' Up (Happy Mix)\\ 05 The Beatsquad - Listen To The Rythm\\ 05 Happy Tunes \& Alchemix - Feel So Good '96\\ 06 Phase - Morning Light\\ 06 The Unknown Project - Can't Get Enough of Hardcore\\ 07 Solid Base - Prison Wall\\ 07 DJ Promo - I Wanna Freak You (Remix)\\ 08 Davie Forbes - Every Single Day\\ 08 Highlander - Roughneck (Original Mix)\\ 09 Happy Tunes - Positive Energy\\ 09 Attaboy - For America\\ 10 DJ Ham, Derno \& Justin Time - Here I Am\\ 10 DJ Yves - Losing Track of Time\\ 11 Cherrish - Confusion\\ 11 Highlander - Last Forever\\ 12 Michaelangelo - The Beat Is Strong\\ 12 Dream Your Dream - XTC\\ 13 DJ E-Rick \& Tactic - Wanna Dance ?\\ 13 Gab - You Better Watch Yourself (Doom of Dance Mix)\\ 14 DJ Tails \& Noizer - Make You Dance\\ 14 DJ Attic \& DJ Stylzz - Fiesta Del Meerty\\ 15 Creasemaster And Slamdog - Big Oh'Booty\\ 15 DJ Delirium - The Party Starter\\ 16 Solid Base - Pumpin'\\ 16 DJ The Prophet - Out on The Streets\\
\\
 \subsection*{Hardstyle}
 \large Slam Hardstyle Vol. 5-6-7 \normalsize\\
 01 Headhunterz ft Krewella - United Kids Of The World\\ 01 Code Black \& Atmozfears - Accelerate (Official XXlerator 2014 Anthem)\\ 01 Wildstylez ft Noah Jacobs - Falling To Forever\\ 02 Omegatypez - Get Up!\\ 02 Bass Modulatorz ft Vice - Save The Day\\ 02 Omegatypez - Good Love\\ 03 Armin Van Buuren - Shivers (Frontliner Remix)\\ 03 Neilio ft Melissa Pixel - Forever\\ 03 Crystal Lake - Welcome To The Zoo\\ 04 Dillytek - Our Legacy\\ 04 Toneshifterz - Wild Wild Weekend (The Qontinent 2014 Anthem)\\ 04 Brennan Heart - Never Break Me (Toneshifterz Remix)\\ 05 Max Enforcer - Lost In Paradise\\ 05 D-Block \& S-te-Fan \& Isaac feat. Chris Madin - Alive\\ 05 Betavoice - I'm Born\\ 06 D-Block \& S-te-fan - Built This City\\ 06 Cybernatics - Astrology\\ 06 Noisecult - This Feeling\\ 07 Noisecontrollers - Around The World\\ 07 Noisecontrollers - Static\\ 07 Frontliner - Somebody Say Yeah\\ 08 Coone \& Substance One - Drowning\\ 08 Atmozfears \& Adrenalize - She Goes\\ 08 The Vision - Visions Of Hardstyle\\ 09 Juized \& Envine - Galaxy\\ 09 Wasted Penguinz - All For Nothing (Vocal Extended Mix)\\ 09 Da Tweekaz feat. MC V - Zero Fucks Given\\ 10 Coone ft Scope DJ - Traveling (Da Tweekaz Remix)\\ 10 Chain Reaction - Barricade\\ 10 Hardwell ft Matthew Koma - Dare You (Audiotricz Remix)\\ 11 Audiotricz - Reborn\\ 11 Alpha - Senses\\ 11 The Anarchist - Loud Noizes\\ 12 A-Lusion \& Cold Case - Set U Free\\ 12 Bass Modulators - Let Me See Ya\\ 12 The Prophet \& The Anarchist ft Rob Gee - IDGAF (I Don't Give A Fuck)\\ 13 TNT - Tarantula\\ 13 Jack Of Sound - Starlight\\ 13 Act Of Rage - Confronting Reality\\ 14 Chris One - Sin City (Phuture Noize Remix)\\ 14 B-Front And Frequencerz feat. MC Nolz - One Of A Kind\\ 14 Frontliner \& Radical Redemption - Frontliner \& Radical Redemption\\ 15 Hard Driver - The Cold Angel (Frequencerz Remix)\\ 15 Stereotuners - Confusion\\ 15 Titan - The One Who Knocks\\ 16 Digital Punk - Invasion\\ 16 Raxtor - Nightfall\\ 16 Frontliner - External Life (The Strangerz Remix)\\ 17 Kold Konexion - Silent Secrets\\ 17 Artic - Ghost\\ 17 Unknown Analoq - Black Out (B-Front Remix)\\ 18 Radical Redemption - Brutal 2.0\\ 18 Thyron - The Return (Total Blackout Anthem 2014)\\ 18 Activator - Cobra\\ 19 Wild Motherfuckers - Natural Born Raver\\ 19 Zany \& Crypsis - C\#NT\\ 19 DJ Thera - Crazy\\ 20 Balistic \& Zero Vision ft Mc Jeff - Upgrade The Noize (Solutio \& The I's Remix)\\ 20 Radical Redemption - Secret Syndicates (Official Beat The Bridge Anthem 2014)\\ 20 B-Front \& Frequencerz - Psycho\\
 01 Wildstylez ft Cimo Frankel - Lights Go Out\\ 01 The Prophet \& Noisecontrollers feat. Leonie Meijer - Make Me Stay\\ 01 Joeysuki \& Kill The BuzZ - Life Is Calling (Wasted Penguinz Remix)\\ 02 Phuture Noize ft Mc DL - Fadin' (Atmozfears Remix)\\ 02 Da Tweekaz \& Atmozfears - Weapons Of Love\\ 02 W\&W \& Ummet Ozcan - The Code (Hard Driver \& Substance One Remix)\\ 03 In-Phase - Here We Go\\ 03 Code Black \& Brennan Heart - Tonight Will Never Die\\ 03 Frontliner - Feels Good Right Here\\ 04 Coone - Magical\\ 04 Max Enforcer - Creatures\\ 04 Audiofreq - Warcry\\ 05 Jack Of Sound - Machine\\ 05 Psyko Punkz - Back Again (Decibel 2014 Anthem)\\ 05 Energyzed - Your Love\\ 06 TNT \& Audiofreq - Screwdriver\\ 06 Tatanka - Your Wake Up Call\\ 06 Raxtor - Impressions\\ 07 D-Block \& S-te-fan - Next Level\\ 07 Code Black - Unleash The Beast (Defqon.1 Australia 2014 Anthem)\\ 07 The Vision - World Eclipse (Neilio Remix)\\ 08 Headhunterz ft Tatu - Colors\\ 08 Audiotricz \& TNT - Ghettoblaster\\ 08 Tuneboy feat. Ruffian - Soym 2K14 RMX\\ 09 Toneshifterz - All On Me\\ 09 Atmozfears \& Adrenalize - Posession\\ 09 Noisecult - Punchlines\\ 10 The Prophet - The Bizz\\ 10 A-Lusion - Are You Ready\\ 10 Da Tweekaz - Intermission\\ 11 Wasted Penguinz - Blinded\\ 11 Outbreak - The Nightmare Factory\\ 11 The Anarchist - Use That Power\\ 12 Gunz For Hire \& Ruffian - Immortal (Qlimax 2013 Anthem)\\ 12 The Prophet \& Adaro - I'm The King\\ 12 The Prophet \& The Anarchist - Dark Matter (Ground Zero 2014 Anthem)\\ 13 Re-Noise - My Style\\ 13 Degos \& Re-Done - Drugs Of Choice\\ 13 D-Block \& S-te-fan \& Mc Villain - Evolutionz (Ran-D Remix)\\ 14 Zatox \& Activator - Make Some Noise\\ 14 Activator \& Ivan Carsten feat. Nikkita - Brutal\\ 14 X-Pander \& Zyprus - Legendary\\ 15 Ran-D \& B-Front - The Message\\ 15 The Anarchist - Raise Hell\\ 15 Neroz - Anguish\\ 16 Coone ft Kritikal - Zombie Killer\\ 16 Stereo Chemists - Mind.Ctrl\\ 16 Exit Mind - Get Down\\ 17 DJ Thera - Celebrate\\ 17 Wildstylez \& Noisecontrollers - Cats, Jets \& Breaks\\ 17 Adaro \& Digital Punk - Natural Born Killers (The Machine Remix)\\ 18 Cold Case - Dreaming\\ 18 Frequencerz \& Alpha2 - Voice Of Gaia\\ 18 B-Front \& Thera - R.E.M. Sleep\\ 19 Kold Konexion - My Case\\ 19 Endymion \& Alpha2 - Mirror Mirror\\ 19 Donkey Rollers - Dream Machine\\ 20 Mark With A K - Darkside (Frequencerz Remix)\\ 20 Kevin Kaos \& Zero Sanity - Hit The Floor (E-Force Remix)\\ 20 B-Front \& Alpha2 - Tormented\\
\end{multicols}
